---
title: "coordination_demand_v6"
format: html
editor: visual
---

# Coordination demand

## Creating a subset on the policy level

```{r}
library(tidyverse)
library(ggplot2)

setwd("/Users/tuva/Documents/Studier/Master/Masteroppgave/r-coding/data/")
load("data_combined.Rda")

data_actors_pol <- data_combined %>% 
  group_by(target_instrument, country, year) %>% 
  summarise(
    n_actors = n_distinct(actor),
    .groups = "drop")

data_coord_pol <- data_combined %>%
  group_by(country, target_instrument, year) %>%
  summarise(
    total_tasks = sum(cum_count),
    simpson = 1 - sum((cum_count / sum(cum_count))^2),
    .groups = "drop")

data_coord_pol <- data_coord_pol %>% 
  left_join(data_actors_pol, by= c("target_instrument", "country","year"))

```

# Creating a theme

```{r}
pub_theme <- function(base_size = 11) {
  theme_minimal(base_size = base_size) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # Frame
    plot.background = element_rect(
      fill = "white",
      colour = "black",
      linewidth = 0.75
    ),
    # Panel
    panel.background = element_rect(fill = "white", 
                                    colour = NA),
    # Axes
    axis.line = element_line(colour = "black", 
                             linewidth = 0.5),
    axis.title = element_text(face = "bold",
                              size = base_size + 1),
    axis.text = element_text(size = base_size),
    
    # LEGEND 
    legend.position = "top",
    legend.direction = "horizontal",
    legend.background = element_rect(
      fill = "white",
      colour = "black",
      linewidth = 0.5
    ),
    legend.title = element_text(face = "bold"),
    legend.key.size = unit(0.75, "lines"),
    legend.margin = margin(5, 5, 5, 5),
    # Caption 
    plot.caption = element_text(
      hjust = 0,
      size = base_size - 1,
      colour = "gray40"
    ),
    # Margin
    plot.margin = margin(10, 10, 10, 10)
  )
}
```

## Descriptive statistics of the variables

### Correlation between number of actors and number of tasks

```{r}

corr_actors_tasks <- ggplot(data_coord_pol, 
                            aes(x = n_actors, 
                           y = total_tasks)) +
  geom_point(position = position_jitter(width = 0.3,
                                        height = 0.3),
             color = "#2C5985",  alpha = .2) +
  labs(
    x = "Number of actors (A)",
    y = "Number of tasks (T)",
    caption = "The figure shows the correlation between the number of actors and the number of tasks in each policy.") +
  theme_light() +
  pub_theme()+
  scale_x_continuous(breaks = seq(0,16,1))

corr_actors_tasks

ggsave("corr_actors_tasks.pdf",
       width = 6,
       height = 4)
```

### Sample distribution n_actors and total_tasks

```{r}
n_actors <- ggplot(data_coord_pol)+
    geom_histogram(aes(x=n_actors))+
    scale_x_continuous(breaks = seq(0,19,1))+
    theme_bw()+
  labs(x = "Number of actors (per policy)")

n_actors

ggsave("n_actors.pdf",
       width = 8,
       height = 6)

n_tasks <- ggplot(data_coord_pol)+
  geom_histogram(aes(x=total_tasks))+
  scale_x_continuous(breaks = seq(0,30,1))+
  theme_bw()+
  labs(x = "Number of tasks (per policy)")

n_tasks

ggsave("n_tasks.pdf",
       width = 8,
       height = 6)
```

## Creating the index

### Function with simpson

```{r}
data_coord_pol2 <- data_coord_pol %>% 
  group_by(target_instrument, country, year) %>% 
  mutate(coord_simp = ((log(n_actors)^3)*simpson)/
           (1+(log(n_actors)^3)*simpson))

names(data_coord_pol2)

table(data_coord_pol2$country)

```

### Function with only log

```{r}
data_coord_pol2 <- data_coord_pol2 %>% 
  group_by(target_instrument, country, year) %>% 
  mutate(coord_log = (log(n_actors)*log(total_tasks))/(1+log(n_actors)*log(total_tasks)))

table(data_coord_pol2$country)

# ggplot(data_coord_pol, aes(x = coord_log))+
#   geom_histogram()+
#   coord_cartesian(xlim = c(0, 1))+
#   theme_light()
# 
# ggplot(data_coord_pol, aes(x = n_actors, 
#                            y = coord_log))+
#   geom_point()+
#   theme_light()+
#   labs(x = "Number of actors",
#     y = "Coordination need (with logT)")+
#   scale_x_continuous(breaks = seq(0,16,2))
```

### Saving the dataset

```{r}
setwd("/Users/tuva/Documents/Studier/Master/Masteroppgave/r-coding/data/")
save(data_coord_pol2, file = "data_coord_pol.Rda")
```

### Creating scenarios

Simpson:

```{r}
library(cartography)

scenarios_simp <- expand.grid(
  n_actors = 1:16,
  simpson = c(0.3, 0.5, 0.7, 0.9)  
) %>%
  mutate(
    coord_simp = (log(n_actors)^3*simpson)/(1+log(n_actors)^3*simpson),
    scenario_label = paste("Simpson =", simpson))

scenarios_simpson <- ggplot(scenarios_simp, aes(x = n_actors, 
                      y = coord_simp, 
                      color = scenario_label)) +
  geom_line(linewidth = 1) +
  labs(
    x = "Number of actors (A)",
    y = "Coordination need (C)",
    color = "Simpson-value",
    caption = "The shows scenarios portraying the relationship between the number of actors and the coordination\n need, given different simpson-values." )+
  theme_light()+
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_color_manual(values = cartography::carto.pal(pal1 = "blue.pal", n1 = 4))+
  pub_theme()

scenarios_simpson

ggsave("scenarios_simpson.pdf",
       width = 7,
       height = 4)

```

logT:

```{r}
scenarios_logT <- expand.grid(
  n_actors = 1:16,
  total_tasks = c(2, 5, 10, 15, 25 )  
) %>%
  mutate(
    coord_log = (log(n_actors)*log(total_tasks))/(1+log(n_actors)*log(total_tasks)),
    scenario_label = factor( 
      paste("T =", total_tasks), 
      levels = paste("T =", c(2, 5, 10, 15, 25))))

scenarios_logT <- ggplot(scenarios_logT, aes(x = n_actors, 
                      y = coord_log, 
                      color = scenario_label)) +
  geom_line(linewidth = 1) +
  labs(
    x = "Number of actors (A)",
    y = "Coordination need (C)",
    color = NULL,
    caption = "Figure B.1 shows scenarios portraying the relationship between the number of actors and the\n coordination need, given different numbers of tasks.") +
  theme_light() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_color_manual(values = cartography::carto.pal(pal1 = "blue.pal", n1 = 5))+
  pub_theme()

scenarios_logT

ggsave("scenarios_logT.pdf",
       width = 7,
       height = 4)

```

### Distributions over time

```{r}
subset_5_years <- data_coord_pol2 %>% 
  filter(year %in% c(1980, 
                     1985,
                     1990, 
                     1995,
                     2000, 
                     2005,
                     2010, 
                     2015,
                     2020))

ggplot(subset_5_years, aes(x = coord_simp)) +
  geom_density() +
  facet_wrap(~ year) +
  theme_minimal()
```

## Number of actors and tasks per year

```{r}
data_coord_pol2 <- data_coord_pol2 %>% 
  mutate(n_actors = as.numeric(n_actors),
         total_tasks = as.numeric(total_tasks),
         simpson = as.numeric(simpson))

data_coord <- data_coord_pol2 %>% 
  group_by(country, year) %>% 
  summarise(actors_mean = mean(n_actors),
            tasks_mean = mean(total_tasks),
            .groups = "drop")

ggplot(data_coord, aes(x=actors_mean, 
                       y=tasks_mean,
                       colour = year))+
  geom_point(position = position_jitter(width = 0.1,
                                        height = 0.1))+
  theme_light()

# Scatterplot of the number of actors and tasks with country-colors:
ggplot(data_coord, aes(x=actors_mean, 
                       y=tasks_mean,
                       colour = country))+
  geom_point(position = position_jitter(width = 0.1,
                                        height = 0.1))+
  theme_light()
```

## Aggregating the index to country-year

```{r}

data_coord2 <- data_coord_pol2 %>% 
  group_by(country, year) %>% 
  summarise(coord_simp_mean = mean(coord_simp),
            coord_log_mean = mean(coord_log),
            coord_simp_sum = sum(coord_simp),
            coord_log_sum = sum(coord_log),
            .groups = "drop")

data_coord <- data_coord %>% 
  left_join(data_coord2, by= c("country", "year"))

coord_simp_plot <- ggplot(data_coord, aes(x=coord_simp))+
  geom_histogram()+
  coord_cartesian(xlim = c(0.25, 0.75))+
  theme_light()

coord_simp_plot

ggsave(coord_simp_plot, file= "coord_simp_plot.pdf")

```

Log T model:

```{r}
coord_log_plot <- ggplot(data_coord, aes(x=coord_log))+
  geom_histogram()+
  coord_cartesian(xlim = c(0.25, 0.75))+
  theme_light()

ggsave(coord_log_plot, file= "coord_log_plot.pdf")
```

## Differentiating the index

```{r}

data_coord <- data_coord %>% 
  group_by(country) %>% 
  arrange(year) %>% 
  mutate(
    coord_simp_sum_lag = dplyr::lag(coord_simp_sum, 1),
    coord_simp_sum_diff = coord_simp_sum - coord_simp_sum_lag
  ) 


data_coord <- data_coord %>% 
  group_by(country) %>% 
  arrange(year) %>% 
  mutate(
    coord_log_sum_lag = dplyr::lag(coord_log_sum, 1),
    coord_log_sum_diff = coord_log_sum - coord_log_sum_lag
  ) 

table(data_coord$country)
```

## Saving the new dataset

```{r}
setwd("/Users/tuva/Documents/Studier/Master/Masteroppgave/r-coding/data/")
save(data_coord, file = "data_coord_cy.Rda")
```
